---
title: "Helka_Lab_02_9041"
author: Katelyn Helka
date: today

---


## Loading Packages

```{r}
#| include: false

library(tidyverse)
library(psych)
library(readxl)
library(gt)
library(janitor)
```

# Loading Data
```{r}
#| include: false

attachment_df <- read_excel("./Attachment_Anxiety_Data.xlsx")

head(attachment_df)
```

# Part 2 of Assignment
## Clean the data:
```{r}
#| include: false

# Cleaning the names of the Data so that I can code it properly. This will remove spaces and make everything to a lowercase letter.
attachment_df_clean <- attachment_df|>
  clean_names() 
```

```{r}
#| include: false

# Cleaning the data to ensure the response variables are all integers and that Gender, Age Group, Relationship Status, and Ethnicity are descriptive rather than the scale response.
attachment_df_clean <- attachment_df_clean |>
  mutate(gender = case_when(gender==1 ~ "Male", gender==2 ~"Female", TRUE ~ "NA")) |>
  mutate(age_group = case_when(age_group == 1 ~ "18-24", age_group == 2 ~ "24-35", age_group == 3 ~ "35-44", age_group == 4 ~ "45-54", age_group == 5 ~ "55-64")) |>
  mutate(relationship = case_when(relationship == 1 ~ "married", relationship == 2 ~ "in a relationship", relationship == 4 ~ "divorced", relationship == 5 ~ "in a relationship", relationship == 6 ~ "never been in a relationship", relationship == 7 ~ "prefer not to say")) |>
  mutate(ethnicity = case_when( ethnicity == 1 ~ "white/Caucasian", ethnicity == 2 ~ "Asian/Asian British", ethnicity == 5 ~ "Other ethnic group", ethnicity == 6 ~ "prefer not to say")) |>
    mutate_at(7:45, as.integer)
```

## Creating an Answer Key
```{r}
#| include: false

answer_key <- list(
  Social_Interaction_Anxitey_Scale = c("sa_1", "sa_2", "sa_3", "sa_4", "-sa_5", "sa_6", "sa_7", "sa_8", "-sa_9", "sa_10", "-sa_11", "sa_12", "sa_13", "sa_14", "sa_15", "sa_16", "sa_17", "sa_18", "sa_19", "sa_20"),
   Experiences_in_Close_Relationships_Scale = c("aa_1", "aa_2", "aa_3", "aa_4", "aa_5", "aa_6", "aa_7", "aa_8", "aa_9"),
  Rosenberg_Self_Esteem_Scale = c("s_est_1", "-s_est_2", "s_est_3", "s_est_4", "-s_est_5", "-s_est_6","s_est_7", "-s_est_8", "-s_est_9", "s_est_10"))
```

## Cronbach's Alpha and average Scores
```{r}
#| include: false

score_social<-scoreItems(answer_key["Social_Interaction_Anxitey_Scale"], attachment_df_clean, totals = F, min=0, max=4)

score_experience<-scoreItems(answer_key["Experiences_in_Close_Relationships_Scale"], attachment_df_clean, totals = F, min=1, max=7)

score_rosenberg<-scoreItems(answer_key["Rosenberg_Self_Esteem_Scale"], attachment_df_clean, totals = F, min=1, max=4)

score_social_df <- as.data.frame(score_social$scores)

score_experience_df <- as.data.frame(score_experience$scores)

score_rosenberg_df <- as.data.frame(score_rosenberg$scores)

all_scores_df <- cbind(score_social_df, score_experience_df, score_rosenberg_df)
```

## Combine the dataframes
```{r}
#| include: false

clean_attachment <- cbind(attachment_df_clean, all_scores_df)

head(clean_attachment)
```
## Reduce Dataframe to what I want
```{r}
#| include: false
attachment_final <- clean_attachment |>
  select("gender", "age_group", "relationship", "ethnicity", "Social_Interaction_Anxitey_Scale", "Experiences_in_Close_Relationships_Scale", "Rosenberg_Self_Esteem_Scale") |>
  mutate_if(is.numeric, round, 2)
```

#Part 2
## Creating a demographic table
```{r}
#| include: false

demographic_table <- attachment_final |>
  tabyl(relationship, age_group)

gttable_1 <- demographic_table |>
  gt() |>
  tab_header(
    title = md("*Distribution of Age Group by Relationship Status*")
  )
```

## Creating a Score Summary Table
```{r}
#| include: false
# Capturing Summary Statistics for certain columns
summary <- describe(select(attachment_final, Social_Interaction_Anxitey_Scale, Experiences_in_Close_Relationships_Scale, Rosenberg_Self_Esteem_Scale))
summary

# Label sample size 
n <- (describe(attachment_final))[1,2]

# Creating a Column in the Summary table labelled "Scales"
Scales <- c("Social_Interaction_Anxitey_Scale", "Experiences_in_Close_Relationships_Scale", "Rosenberg_Self_Esteem_Scale")

summary$Scales<- Scales

# Selecting for only the columns that will appear in the final table
summary <- summary |>
    select(Scales, mean, median, sd, range) |>
       mutate_if(is.numeric, round, 2)

# Combining the three Cronbach's alpha values
alphas <- round(c(score_social$alpha, score_experience$alpha, score_rosenberg$alpha), 2)

# Combine summary information with alpha values
final_reptable <- cbind(summary, alphas)

# Create a reproducible table
gttable_2<- gt(final_reptable) |>
    tab_header(
        title = md("*Descriptive Statistics for Attachment Anxitey in Adults*")) |>
    tab_stubhead(label= "Composites")|>
    tab_spanner(
        label="Central Tendency",
        columns = c(mean, median)
    )|>
        tab_spanner(
        label="Variability",
        columns = c(sd, range)
        )|>
            tab_spanner(
        label = "Reliability Values (Chronbach's alpha)",
    columns = "alphas"
            ) 
```

### Filtered Score Table
```{r}
#| include: false
attachment_filter <- attachment_final |>
    filter(age_group == "24-35")
```

### Creating the Filtered Score Table
```{r}
#| include: false
# Capturing Summary Statistics for certain columns
summary_filter <- describe(select(attachment_filter, Social_Interaction_Anxitey_Scale, Experiences_in_Close_Relationships_Scale, Rosenberg_Self_Esteem_Scale))
summary_filter

# Label sample size 

n_filter <- (describe(attachment_filter))[1,2]

# Creating a Column in the Summary table labelled "Scales"
Scales_filter <- c("Social_Interaction_Anxitey_Scale", "Experiences_in_Close_Relationships_Scale", "Rosenberg_Self_Esteem_Scale")

summary_filter$Scales<- Scales_filter 

# Selecting for only the columns that will appear in the final table
summary_filter <- summary_filter |>
    select(Scales, mean, median, sd, range) |>
       mutate_if(is.numeric, round, 2)

# Combining the three Cronbach's alpha values
alphas_filter <- round(c(score_social$alpha, score_experience$alpha, score_rosenberg$alpha), 2)

# Combine summary information with alpha values
filter_reptable <- cbind(summary_filter, alphas_filter)

# Create a reproducible table
gttable_3<- gt(filter_reptable) |>
    tab_header(
        title = md("*Descriptive Statistics for Attachment Anxitey in Adults ages 24-35*")) |>
    tab_stubhead(label= "Composites")|>
    tab_spanner(
        label="Central Tendency",
        columns = c(mean, median)
    )|>
        tab_spanner(
        label="Variability",
        columns = c(sd, range)
        )|>
            tab_spanner(
        label = "Reliability Values (Chronbach's alpha)",
    columns = "alphas_filter"
            ) 
```

# Intro
## Participants
The sample consisted of `{r} n` adults

`{r} gttable_1`


## Measures
The following scales were used: 

The Social Interaction Anxiety Scale, with a Cronbach's alpha of 
`{r} round(score_social$alpha, 2)`, 

The Experiences in Close Relationships Scale, with an alpha of `{r} round(score_experience$alpha, 2)`, 

The Rosenberg Self-Esteem Scale had an alpha of `{r} round(score_rosenberg$alpha, 2)`.

## Data Analysis Strategy
Items marked with a leading minus sign in the answer key (e.g., `-sa_5`) 
were reverse-keyed before scoring.All items included: 
Items 5, 9, and 11 from the Social Interaction Anxitey Scale and Items 2, 5, 6, 8, and 9 in the Rosenberg Self-Esteem Scale. 

## Results

`{r} gttable_2`

Across the full sample, the mean Social Interaction Anxiety score was 
`{r} final_reptable$mean[1]`, the mean Experiences in Close Relationships 
score was `{r} final_reptable$mean[2]`, and the mean Rosenberg Self-Esteem 
score was `{r} final_reptable$mean[3]`.

`{r} gttable_3`

Among participants aged 24–35, the mean Social Interaction Anxiety score was 
`{r} filter_reptable$mean[1]`, the mean Experiences in Close Relationships 
score was `{r} filter_reptable$mean[2]`, and the mean Rosenberg Self-Esteem 
score was `{r} filter_reptable$mean[3]`.